Re-finding to support a Deep Web Question Answering System

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
general editing

The largest limitation to our current work is the QRR.  In order to efficiently answer new user questions the systems needs a large amount of user annotated queries.  However, a significant amount user interaction is required to understand the answer retrieval process.  By continuing to studying the methods of user data collection we plan to develop a model to support a unsupervised question resolution process.  This will increase the scalability and efficiency of the system.

Because each QRM may be treated as a function, we plan on leveraging previous work to allow new questions to be solved by connecting together several QRMs \cite{morpheus1, transformscout}.  This method would expand the types of queries that are answerable be the system.

Currently, the category hierarchy that is generated from the DBpedia categories and our SSQ ontologies are stored in separate XML files. We are in the process of storing these ontologies into an efficient ontology database. Similarly, employing user input brings about the likelihood that redundant SSQ ontological elements will be inserted into our ontology store. We are working on merging the similar SSQs [\ref{sec:ssq}] based on the SSQ realms and other ontological structural information so that we can remove the redundancy in the database.

In addition, we cannot fully depend on the DBpedia categories, since the relevant data available in DBpedia store is insufficient to represent the real world queries belongs to all the realms. [e.g. musical bands]. We are planning to define new categories from the deep web [or find out new sources to fill those \textit{weak} realms] in our ontology hierarchy.

@@

In this paper we provide a discussion on a new type of question answering system that uses previously answered questions user.  We described our method of modeling a users question answering process and how we are able to discover semantically similar queries.

>>>>

The greatest limitation to our current work is the diversity of the QRR.  In order to efficiently answer new user questions the systems needs a large amount of user annotated queries.  However, a significant number of user interactions is required to understand the answer retrieval process.  By continuing to study the methods of user data collection we plan to develop a model to support an unsupervised question resolution process.  This will increase the scalability and efficiency of the system.

Because each QRM may be treated as a function, we plan on leveraging previous work to allow new questions to be solved by connecting together several QRMs \cite{morpheus1, transformscout}.  This method would expand the types of queries that are answerable by the system.

Currently, the category heterarchy generated from the DBpedia categories and our SSQ ontologies is stored in separate XML files. We are in the process of moving these ontologies into an efficient ontology database. Similarly, employing user input brings about the likelihood that redundant SSQ ontological elements will be inserted into our ontology store. We are working on merging the similar SSQs [\ref{sec:ssq}] based on the SSQ realms and other ontological structural information so that we can remove the redundancy in the database.

In addition, we cannot fully depend on the DBpedia categories, since the relevant data available in DBpedia store is insufficient to represent the real world queries belonging to all realms. [e.g. musical bands]. We are planning to define new categories from the deep web [or find out new sources to fill those \textit{weak} realms] in our ontology hierarchy.

@@

In this paper we provide a discussion on a new type of question answering system that uses previously answered user questions.  We described our method of modeling a users question answering process and how we are able to discover semantically similar queries.
